An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2012-03-30 mc.Rnw
Drafted initial version of the paper

We will also conduct a brief Monte Carlo experiment to demonstrate
that this modified statistic performs essentially the same as Clark
and West's.  We draw observations from their \dgp\ 1:

\begin{gather*}
  y_t = 0.5 + \gamma^{*} z_{t-1} + e_t \qquad\qquad
  z_t = 0.15 + 0.95 z_{t-1} + v_t \\
  (e_t, v_t)' \sim iid\ N(0, \begin{pmatrix} 18 & - 0.5 \\ \cdot & 0.025 \end{pmatrix}.
\end{gather*}
Both models are estimated by \ols. The benchmark model regresses $y_t$
on a constant, and the alternative regresses $y_t$ on a constant and
$z_{t-1}$.  We run the same size and power simulations as
\citet{ClW:07}; $\gamma^{*}$ equals zero for the size simulations and
0.35 in the power simulations.

>>>>

<<echo=F>>=
library(dbframe)
library(xtable)
mcdata1 <- dbframe("dgp1", "mcdata.db")
mcdata2 <- dbframe("dgp2", "mcdata.db")
groups <- c( "isPower", "R", "P")
size <- .1

printbooktabs <- function(x,...){
  print(xtable(x,...),
        floating=F,
        hline.after=NULL, 
        add.to.row=list(pos=list(-1,0, nrow(x)), 
          command=c(
            '\\toprule ',
            '\\midrule ',
            '\\bottomrule ')),...)
}

fspace <- function(x) gsub(" ", "\\\\enskip", format(round(x, 1)))

printall <- function(mcdb,...) {
  d <- subset(select(mcdb, group.by = groups, 
                     sprintf(c("case isPower when 0 then 'size' else 'power' end as 'type'",
                               "R", "P", 
                               "100 * avg(pOld <= %f) as 'Pr[CW]'",
                               "100 * avg(pNew1 <= %f) as 'Pr[New]'",
                               "100 * (avg(pOld <= %f and pNew1 > %f) + avg(pOld > %f and pNew1 <= %f)) as 'Pr[tests disagree]'"),
                             size, size, size, size)), select = -isPower)
  d$R <- fspace(d$R)
  d$P <- fspace(d$P)
  d[[4]] <- fspace(d[[4]])
  d[[5]] <- fspace(d[[5]])
  d[[6]] <- fspace(d[[6]])
  d$R[duplicated(subset(d, select = c(type, R)))] <- NA
  d$type[duplicated(d$type)] <- NA
  printbooktabs(d, include.rownames = FALSE, digits = c(0,0,0,0,1,1,1), 
                align = c("l","l","c","c","c","c","c"), 
                sanitize.text.function = function(x) x)
}
@ 
We will also conduct two brief Monte Carlo experiments to demonstrate
that this modified statistic performs similarly to
\possessivecite{ClW:07}.  We'll use both of the \dgp s they consider.
For the first, we have
\begin{align}\label{eq:dgp1}\tag{\dgp\ 1}
  y_t &= 0.5 + \gamma^{*} z_{t-1} + e_t &
  \gamma^{*} &=
  \begin{cases}
    0 & \text{size simulations} \\
    0.35 & \text{power simulations}
  \end{cases}\\\nonumber
  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
  \end{pmatrix}
   , \begin{pmatrix} 18 & -
    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
\end{align}
Both models are estimated by \ols. The benchmark model regresses $y_t$
on a constant, and the alternative regresses $y_t$ on a constant and
$z_{t-1}$.  We use both \poscw\ original statistic and our new
statistic to test the null that the benchmark model's innovation is an
\mds.\footnote{\citet{ClW:07} report the performance of the tests
  proposed by \citet{CCS:01} and \citet{ClM:05} as well, and of tests
  based on the naive Gaussian statistic.}

\begin{table}[tb]
  \centering
<<mc1, echo=F, results=tex>>=
printall(mcdata1)
@ 
\caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
  10\% confidence.  These percentages are calculated from 5000
  samples.  Pr[CW] shows the fraction of simulations for which Clark
  and West's (2007) statistic rejects; Pr[New] shows the fraction of
  simulations for which this paper's test rejects; and Pr[tests
  disagree] gives the fraction of simulations in which this paper's
  test and Clark and West's (2007) give different conclusions.}
\label{tab:mc1}
\end{table}

The second \dgp\ is
\begin{align} \label{eq:dgp2}\tag{\dgp\ 2}
  y_{t} &= 2.237 + 0.261 + \gamma^{*}_{1} z_{t-1} + \gamma_{2}^{*}
  z_{t-2} + \gamma_{3}^{*} z_{t-3} + \gamma_{4}^{*} z_{t-4} + e_{t} \\
  z_{t} &= 0.804 z_{t-1} - 0.221 z_{t-2} + 0.226 z_{t-3} - 0.205
  z_{t-4} + v_{t} \nonumber \\
  \binom{e_{t}}{v_{t}} &\sim N\Bigg(
  \begin{pmatrix}
    0 \\ 0
  \end{pmatrix},
  \begin{pmatrix}
    10.505 & 1.036 \\ 1.036 & 0.366
  \end{pmatrix}
  \Bigg) \nonumber\\\nonumber
  \gamma^{*} &=
  \begin{cases}
    0 & \text{size simulations}\\
    (3.363, -0.633, -0.377, -0.529)' & \text{power simulations}.
  \end{cases}
\end{align}
The benchmark model for $y_{t}$ is an AR(1) and the alternative model
includes all four lags of $z_{t}$.  For this simulation, $R$ is 80 or
120 and $P$ is 40, 80, 120, or 160.  \citet{ClW:07} argue that the
first \dgp\ mimics an asset pricing application and the second mimics
\gdp\ growth forecasting using the Federal Reserve Bank of Chicago's
National Activity Index.

\begin{table}[tb]
  \centering
<<mc2, echo=F, results=tex>>=
printall(mcdata2)
@ 
\caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
  10\% confidence.  These percentages are calculated from 5000
  samples.  Pr[CW] shows the fraction of simulations for which Clark
  and West's (2007) statistic rejects; Pr[New] shows the fraction of
  simulations for which this paper's test rejects; Pr[tests disagree]
  gives the fraction of simulations in which this paper's test and
  Clark and West's (2007) give different conclusions.}
\label{tab:mc2}
\end{table}

Table~\ref{tab:mc1} presents the simulation results
for~(\ref{eq:dgp1}) and Table~\ref{tab:mc2} for~(\ref{eq:dgp2}).  For
all of the parameter values, our proposed new statistic has slightly
lower rejection probability than \possessivecite{ClW:07}.  For both
\dgp s the statistics are slightly undersized.  In~\eqref{eq:dgp1},
this translates to relatively low power and the power difference
between the two statistics may be noticeable.  In~\eqref{eq:dgp2},
though, the evidence against the benchmark is strong enough under the
alternative that the tests reject almost all of the time.  In that
setting, the lower power of our new test is essentially irrelevant.

%%% Local Variables:
%%% TeX-master: "Paper"
%%% End:
% LocalWords:  dbframe xtable mcdata dgp printbooktabs hline pos nrow toprule
% LocalWords:  midrule bottomrule printall mcdb dsize isPower sprintf pOld pNew
% LocalWords:  dpower qs dadj dfapply rownames tb tex oos eqref eq mc ClW dgp's
% LocalWords:  possessivecite nonumber sim iid Bigg binom pmatrix ols poscw CCS
% LocalWords:  ClM
